Thesis Title

### 2022-03-22 main.tex
add table 2 chap 2
finish introduction first draft
update citation style
Updates from Overleaf

%-----------------------------------------------------------------
% Packages
%------------------------------------------------------------------
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\thechapter. #1 }}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\usepackage{titlesec}
\fancyhf{}
\fancyhead[RO]{\bfseries\rightmark}
\fancyhead[LE]{\bfseries\leftmark}
\setlength{\headheight}{15pt}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\headheight}{0.5pt}
\fancypagestyle{plain}{
  \fancyhead{}
  \renewcommand{\headrulewidth}{0pt}
}
\usepackage{hyperref} % To add urls
\usepackage{graphicx} % To add images
\usepackage[nottoc]{tocbibind}
\usepackage[backend=biber,style=authoryear,maxcitenames=1,autocite=inline,natbib=true,sorting=nty]{biblatex} % References
\addbibresource{references.bib}
\usepackage{indentfirst} % Add indentation to first paragraph
\setlength{\parskip}{1em}
\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}
\usepackage{enumitem}
\usepackage[font=footnotesize]{caption}
\usepackage[toc,page]{appendix}
\usepackage{pdfpages}
\usepackage{fmtcount}
\usepackage{url}
\usepackage{amsmath}
\usepackage{bm}
\usepackage[utf8]{inputenc}
\usepackage{filecontents}
\usepackage{float}
\raggedbottom
\usepackage{subcaption}
\usepackage{eurosym}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage[acronym]
\makeatletter
\def\cleardoublepage{\clearpage\if@twoside \ifodd\c@page\else
    \hbox{}
    \thispagestyle{plain}
    \newpage
    \if@twocolumn\hbox{}\newpage\fi\fi\fi}
\makeatother \clearpage{\pagestyle{plain}\cleardoublepage}

\providecommand{\keywords}[1]{\textbf{Keywords:} #1}
\providecommand{\keywordsP}[1]{\textbf{Palavras chave:} #1}
\newcommand{\secref}[1]{\autoref{#1}. \nameref{#1}}
\usepackage{lscape}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{graphicx}

@@

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/paper1}
\newpage
\printbibliography
\end{refsection}

>>>>

%-----------------------------------------------------------------
% Packages
%------------------------------------------------------------------
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\thechapter. #1 }}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\usepackage{titlesec}
\fancyhf{}
\fancyhead[RO]{\bfseries\rightmark}
\fancyhead[LE]{\bfseries\leftmark}
\setlength{\headheight}{15pt}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\headheight}{0.5pt}
\fancypagestyle{plain}{
  \fancyhead{}
  \renewcommand{\headrulewidth}{0pt}
}
\usepackage{hyperref} % To add urls
\usepackage{graphicx} % To add images
\usepackage[nottoc]{tocbibind}
\usepackage[backend=biber,style=numeric-comp,maxcitenames=1,autocite=inline,natbib=true,sorting=none]{biblatex} % References
\addbibresource{references.bib}
\usepackage{indentfirst} % Add indentation to first paragraph
\setlength{\parskip}{1em}
\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}
\usepackage{enumitem}
\usepackage[font=footnotesize]{caption}
\usepackage[toc,page]{appendix}
\usepackage{pdfpages}
\usepackage{fmtcount}
\usepackage{url}
\usepackage{amsmath}
\usepackage{bm}
\usepackage[utf8]{inputenc}
\usepackage{filecontents}
\usepackage{float}
\raggedbottom
\usepackage{subcaption}
\usepackage{eurosym}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage[acronym]
\makeatletter
\def\cleardoublepage{\clearpage\if@twoside \ifodd\c@page\else
    \hbox{}
    \thispagestyle{plain}
    \newpage
    \if@twocolumn\hbox{}\newpage\fi\fi\fi}
\makeatother \clearpage{\pagestyle{plain}\cleardoublepage}

\providecommand{\keywords}[1]{\textbf{Keywords:} #1}
\providecommand{\keywordsP}[1]{\textbf{Palavras chave:} #1}
\newcommand{\secref}[1]{\autoref{#1}. \nameref{#1}}
\usepackage{lscape}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{multirow}
\hypersetup{hidelinks}

@@

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_2}
\newpage
\printbibliography
\end{refsection}

%-----------------------------------------------------------------
% Paper 2
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{Detection of a novel \textit{mcr-5.4} gene variant in hospital tap water by shotgun metagenomic sequencing\label{ch:paper2}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_3}
\newpage
\printbibliography
\end{refsection}
